Taylor \& Francis Rmarkdown template for authors (\LaTeX-based \textsf{Interact} layout + Chicago author-date reference style)

### 2022-04-20 paper_comparsion/paper_comparision/paper_comparision.Rmd
add test

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are refereed to as standard residual plots. They are commonly used to identify patterns which are indicative of nonconstant error variance or nonlinearity [@cook1982residuals]. Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used always present. While raw residuals are the most common output of computer regression software package, by applying a scaling factor, the ability of revealing nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst2018regression].

@@

<!-- large sample size-->
Overlapping data points is a general issue in scatter plots not limited to standard residual plots, which often makes plots difficult to interpret because visual patterns are concealed. Thus, for relatively large sample size, @cleveland1975graphical suggests the use of robust reference lines to give aids to eye in seeing patterns, which nowadays, are usually replaced with a spline or local polynomial regression line.

One of the useful supplements to standard residual plots is partial residual plot. While the standard residual plots indicate deviations of each predictor from linearity, the partial residual plots can be used to access the extent and the direction of the linearity. These plots can therefore be used to determine the importance of each predictor in the presence of all the others and assess the extent of nonlinearity in a given predictor. This is in addition to providing information on correct transformations and extreme data points.

>>>>

## Data plots

Data plots are one of the most important and preferred methods of regression diagnostics. Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are refereed to as standard residual plots. They are commonly used to identify patterns which are indicative of nonconstant error variance or nonlinearity [@cook1982residuals]. Raw residuals and studentized residuals are the two most frequently used residuals in standard residual plots. The debt on which type of residuals should be used always present. While raw residuals are the most common output of computer regression software package, by applying a scaling factor, the ability of revealing nonconstant error variance in standard residual plots will often be enhanced by studentized residuals in small sample size [@gunst2018regression].

@@

<!-- large sample size-->
Overlapping data points is a general issue in scatter plots not limited to standard residual plots, which often makes plots difficult to interpret because visual patterns are concealed. Thus, for relatively large sample size, @cleveland1975graphical suggests the use of robust moving statistics as reference lines to give aids to eye in seeing patterns, which nowadays, are usually replaced with a spline or local polynomial regression line.

Other types of data plots that are often used in regression diagnostics include partial residual plots and probability plots. Partial residual plots are useful supplements to standard residual plots as they provide additional information on the direction of linearity as well as the nonlinearity of each predictor. Probability plots can be used to compare the sampling distribution of the residuals to the normal distribution.

## Hypothesis testing

### 2022-04-20 paper_comparsion/paper_comparision/paper_comparision.tex
add test

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are refereed to as standard residual plots. They
are commonly used to identify patterns which are indicative of
nonconstant error variance or nonlinearity \citep{cook1982residuals}.
Raw residuals and studentized residuals are the two most frequently used
residuals in standard residual plots. The debt on which type of
residuals should be used always present. While raw residuals are the
most common output of computer regression software package, by applying
a scaling factor, the ability of revealing nonconstant error variance in
standard residual plots will often be enhanced by studentized residuals
in small sample size \citep{gunst2018regression}.

@@

Overlapping data points is a general issue in scatter plots not limited
to standard residual plots, which often makes plots difficult to
interpret because visual patterns are concealed. Thus, for relatively
large sample size, \citet{cleveland1975graphical} suggests the use of
robust reference lines to give aids to eye in seeing patterns, which
nowadays, are usually replaced with a spline or local polynomial
regression line.

One of the useful supplements to standard residual plots is partial
residual plot. While the standard residual plots indicate deviations of
each predictor from linearity, the partial residual plots can be used to
access the extent and the direction of the linearity. These plots can
therefore be used to determine the importance of each predictor in the
presence of all the others and assess the extent of nonlinearity in a
given predictor. This is in addition to providing information on correct
transformations and extreme data points.

>>>>

\hypertarget{data-plots}{%
\subsection{Data plots}\label{data-plots}}

Data plots are one of the most important and preferred methods of
regression diagnostics. Graphical summaries in which residuals are
plotted against fitted values or other functions of the predictor
variables that are approximately orthogonal to residuals are refereed to
as standard residual plots. They are commonly used to identify patterns
which are indicative of nonconstant error variance or nonlinearity
\citep{cook1982residuals}. Raw residuals and studentized residuals are
the two most frequently used residuals in standard residual plots. The
debt on which type of residuals should be used always present. While raw
residuals are the most common output of computer regression software
package, by applying a scaling factor, the ability of revealing
nonconstant error variance in standard residual plots will often be
enhanced by studentized residuals in small sample size
\citep{gunst2018regression}.

@@

Overlapping data points is a general issue in scatter plots not limited
to standard residual plots, which often makes plots difficult to
interpret because visual patterns are concealed. Thus, for relatively
large sample size, \citet{cleveland1975graphical} suggests the use of
robust moving statistics as reference lines to give aids to eye in
seeing patterns, which nowadays, are usually replaced with a spline or
local polynomial regression line.

Other types of data plots that are often used in regression diagnostics
include partial residual plots and probability plots. Partial residual
plots are useful supplements to standard residual plots as they provide
additional information on the direction of linearity as well as the
nonlinearity of each predictor. Probability plots can be used to compare
the sampling distribution of the residuals to the normal distribution.

\hypertarget{hypothesis-testing}{%
\subsection{Hypothesis testing}\label{hypothesis-testing}}
